Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2023-09-26 analysis/paper/paper.qmd
changed dpi of the figures.

# ggsave(here::here("analysis/figures/fig-map.jpg"),
#        width = 4,
#        height = 4.5,
#        units = "in",
#        dpi = 400)
```

@@

# ggsave(here::here("analysis/figures/fig-tcsa-all-sp.jpg"),
#        width = 4.45,
#        height = 4.5,
#        units = "in",
#        dpi = 400)

@@

# ggsave(here::here("analysis/figures/fig-artifact-size-cluster.jpg"),
#        width = 4,
#        height = 4,
#        units = "in",
#        dpi = 400)

@@

# ggsave(here::here("analysis/figures/fig-tcsa-raw-materials.jpg"),
#        width = 4.3,
#        height = 2.7,
#        units = "in",
#        bg = "white",
#        dpi = 400)
```

@@

# ggsave(here::here("analysis/figures/fig-tcsa-size.jpg"),
#        width = 4,
#        height = 3.3,
#        units = "in",
#        dpi = 400)

@@

# ggsave(here::here("analysis/figures/fig-tcsa-radio-carbon.jpg"),
#        width = 4,
#        height = 4.5,
#        units = "in",
#        bg = "white",
#        dpi = 400)

@@

# ggsave(here::here("analysis/figures/fig-tcsa-per-sites.jpg"),
#        width = 4.3,
#        height = 3,
#        units = "in",
#        bg = "white",
#        dpi = 400)
```

@@

# ggsave(here::here("analysis/figures/fig-gis-tcsa-sitess.jpg"),
#        width = 4,
#        height = 6,
#        units = "in",
#        bg = "white",
#        dpi = 400)

>>>>

# ggsave(here::here("analysis/figures/fig-map.jpg"),
#        width = 4,
#        height = 4.5,
#        units = "in",
#        dpi = 300)
```

@@

# ggsave(here::here("analysis/figures/fig-tcsa-all-sp.jpg"),
#        width = 4.45,
#        height = 4.5,
#        units = "in",
#        dpi = 300)

@@

# ggsave(here::here("analysis/figures/fig-artifact-size-cluster.jpg"),
#        width = 4,
#        height = 4,
#        units = "in",
#        dpi = 300)

@@

# ggsave(here::here("analysis/figures/fig-tcsa-raw-materials.jpg"),
#        width = 4.3,
#        height = 2.7,
#        units = "in",
#        bg = "white",
#        dpi = 300)
```

@@

# ggsave(here::here("analysis/figures/fig-tcsa-size.jpg"),
#        width = 4,
#        height = 3.3,
#        units = "in",
#        dpi = 300)

@@

# ggsave(here::here("analysis/figures/fig-tcsa-radio-carbon.jpg"),
#        width = 4,
#        height = 4.5,
#        units = "in",
#        bg = "white",
#        dpi = 300)

@@

# ggsave(here::here("analysis/figures/fig-tcsa-per-sites.jpg"),
#        width = 4.3,
#        height = 3,
#        units = "in",
#        bg = "white",
#        dpi = 300)
```

@@

# ggsave(here::here("analysis/figures/fig-gis-tcsa-sites.jpg"),
#        width = 4,
#        height = 6,
#        units = "in",
#        bg = "white",
#        dpi = 300)
